Running an open experiment: transparency and reproducibility in soil and ecosystem

### 2016-05-18 manuscript_openexperiment/Open_experiment.Rmd
Initial ERL submission

Science is becomingly increasingly collaborative and data-intensive {Adams, 2012 #4348}; in conjunction with revolutions in Internet-based communication, this has created new research opportunities across former geographic and disciplinary barriers. At the same time, many factors are pushing scientists to increase data access and use "best practices" in dealing with data and code {Hart, 2015 #4292;Wilson, 2014 #4337}.

>>>>

Science is becoming increasingly collaborative and data-intensive {Adams, 2012 #4348}; in conjunction with revolutions in Internet-based communication, this has created new research opportunities across former geographic and disciplinary barriers. At the same time, many factors are pushing scientists to increase data access and use "best practices" in dealing with data and code {Hart, 2015 #4292;Wilson, 2014 #4337}.
